A large-scale study of polymorphism in R

### 2019-03-16 paper/main.tex
intro

@@

Our community is centred on building, improving, and reasoning about
programming languages.  A key component in all this is to truly
\textit{understand} the languages we're working on, so that we may make the
best decisions for the benefit of all users of a programming language.  In
many cases, we as researchers can appeal to our own intuition to at least
build a sense for how a language is used, as language users typically have
some training from an experienced programmer or software engineer (e.g.,
computer science studies, online tutorials written by language experts,
etc.).  \AT{We claim that this is emphatically not the case in R.}

>>>>

Our community builds, improves, and reasons about programming languages.  To
make design decisions that benefit most users of a language, we need to
understand the language we are working with as well as the real-world needs
it answers. Often, we, as researchers, can appeal to our intuition as many
languages are intended to be general purpose and appeal to users with some 
training.

@@
